---
title: "UP 592: Doctoral Urban Planning Seminar"
subtitle: "Fall 2026 & Spring 2027"
---

## Welcome

The Doctoral Urban Planning seminar is a platform for the intellectual development of PhD students in the Department of Urban & Regional Planning. The seminar provides a shared space for students to present their research and to solicit critical, yet constructive, peer reviews and advice.

```{r}
#| label: cycle-setup
#| include: false

source("R/cycle-diagram.R")

# ── Which phase is this semester? ───────────────────────────────────────────
# The diagram is generated from this; nothing else needs editing when the
# rotation advances. Standalone copies for slides/handouts:
#   Rscript scripts/build-cycle-diagrams.R
current_phase <- 1
semester      <- "Fall 2026"
```

## The Seminar Cycle

The seminar is built around a **four-semester cycle** of workshops. Students cycle through all four phases during their pre-candidacy coursework.

```{r}
#| label: cycle-diagram
#| echo: false
#| results: asis
cat(cycle_diagram_svg(current_phase, semester))
```

::: {.callout-note}
## Current Semester: `r semester`

This semester focuses on **Writing Your First Article** — developing publishable scholarship from coursework and early research.
:::

## Quick Links

- **[Syllabus](syllabus.qmd)** — Course information, policies, and expectations
- **[Schedule](schedule.qmd)** — Week-by-week session plans for Fall 2026 and Spring 2027
- **[Resources](resources.qmd)** — Links, templates, and tools for doctoral students

## This Semester at a Glance

**Fall 2026: Writing Your First Article**

- 5 core workshops on article writing, journal targeting, argumentation, peer review, and co-authorship
- 5 rounds of peer presentations — informal, low-stakes research-in-progress talks
- ACSP conference prep in Week 8
- Annual CV check-in built into Week 1

**Spring 2027: Writing Your Dissertation Proposal**

- 5 core workshops on proposal structure, theoretical frameworks, methods, timelines, and defense strategies
- Milestone presentations — Plan of Study, updated plans, and QRP/Exam content
- ICUA/UAA conference prep in Week 13

---

*Last updated: July 2026*
