---
title: "Schedule"
subtitle: "Week-by-week session plans"
---

```{r}
#| label: setup
#| include: false

# ─────────────────────────────────────────────────────────────────────────────
# SCHEDULE PARAMETERS
#
# Dates are DERIVED, not typed. To move the seminar to a different day or week,
# change the start date below and re-render — every row shifts with it.
# The meeting day shown in each phase header is read back off the start date,
# so a wrong day is visible on the page rather than buried in a table.
# ─────────────────────────────────────────────────────────────────────────────

source("R/course-meta.R")
fall_start   <- FALL_START
spring_start <- SPRING_START

# Session type -> CSS badge class (see styles.css)
badge_class <- c(
  Workshop     = "badge-core",
  Presentation = "badge-presentation",
  Milestone    = "badge-milestone",
  Student      = "badge-student",
  Synthesis    = "badge-synthesis",
  Conference   = "badge-conference",
  Break        = "badge-break"
)

# Build a schedule table: dates are start + 7 * (week - 1)
build_schedule <- function(start, sessions) {
  dates <- start + 7 * (seq_len(nrow(sessions)) - 1)
  stopifnot(all(sessions$Type %in% names(badge_class)))
  data.frame(
    Week  = seq_len(nrow(sessions)),
    Date  = trimws(format(dates, "%b %e")),
    Type  = sprintf('<span class="%s">%s</span>',
                    badge_class[sessions$Type], sessions$Type),
    Topic = sessions$Topic,
    Lead  = sessions$Lead,
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
}

source("R/sessions.R")

tbl <- function(df) {
  knitr::kable(df, escape = FALSE, align = c("c", "l", "l", "l", "l"))
}
```

## Fall 2026

::: {.phase-header}
### Phase 1: Writing Your First Article
`r meeting_line(fall_start)`<br>`r date_span(fall_start, nrow(fall_sessions))`
:::

```{r}
#| label: fall-schedule
#| echo: false
tbl(build_schedule(fall_start, fall_sessions))
```

**Notes:** Core workshops alternate with student presentations. No seminar the week of ACSP (Oct 8&ndash;10, Pittsburgh); conference prep runs the week before. Week 13 is reserved for student-determined content. The final session connects fall article work to spring proposal development.

---

## Spring 2027

::: {.phase-header}
### Phase 3: Writing Your Dissertation Proposal
`r meeting_line(spring_start)`<br>`r date_span(spring_start, nrow(spring_sessions))`
:::

```{r}
#| label: spring-schedule
#| echo: false
tbl(build_schedule(spring_start, spring_sessions))
```

**Notes:** Milestone sessions accommodate both QRP and qualifying exam students. No seminar over spring break, or the week of ICUA/UAA (Apr 14&ndash;16, New York); presentation practice runs the week before. Week 14 is reserved for student-determined content. The seminar serves first- and second-year students together — Cohort A milestones are second-year work, Cohort B first-year.

---

## Session Types

- **<span class="badge-core">Workshop</span>** — Facilitated session on the semester's phase topic
- **<span class="badge-presentation">Presentation</span>** — Informal research-in-progress talk
- **<span class="badge-milestone">Milestone</span>** — Formal milestone presentation (Plan of Study, QRP, etc.)
- **<span class="badge-student">Student</span>** — Content determined by seminar participants
- **<span class="badge-conference">Conference</span>** — Conference preparation and presentation practice
- **<span class="badge-synthesis">Synthesis</span>** — Semester opening or closing session; reflection and forward planning
- **<span class="badge-break">Break</span>** — No seminar (holiday or conference)

---

*Schedule subject to change based on student needs and conference dates.*
