---
title: "Schedule"
subtitle: "Week-by-week session plans"
---

```{r}
#| label: setup
#| include: false

# ─────────────────────────────────────────────────────────────────────────────
# SCHEDULE PARAMETERS
#
# Dates are DERIVED, not typed. To move the seminar to a different day or week,
# change the start date below and re-render — every row shifts with it.
# The meeting day shown in each phase header is read back off the start date,
# so a wrong day is visible on the page rather than buried in a table.
# ─────────────────────────────────────────────────────────────────────────────

source("R/course-meta.R")
fall_start   <- FALL_START
spring_start <- SPRING_START

# Session type -> CSS badge class (see styles.css)
badge_class <- c(
  Workshop     = "badge-core",
  Presentation = "badge-presentation",
  Milestone    = "badge-milestone",
  Student      = "badge-student",
  Synthesis    = "badge-synthesis",
  Conference   = "badge-conference",
  Break        = "badge-break"
)

# Build a schedule table: dates are start + 7 * (week - 1)
build_schedule <- function(start, sessions) {
  dates <- start + 7 * (seq_len(nrow(sessions)) - 1)
  stopifnot(all(sessions$Type %in% names(badge_class)))
  data.frame(
    Week  = seq_len(nrow(sessions)),
    Date  = trimws(format(dates, "%b %e")),
    Type  = sprintf('<span class="%s">%s</span>',
                    badge_class[sessions$Type], sessions$Type),
    Topic = sessions$Topic,
    Lead  = sessions$Lead,
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
}

s <- function(type, topic, lead) {
  data.frame(Type = type, Topic = topic, Lead = lead,
             stringsAsFactors = FALSE)
}

fall_sessions <- rbind(
  s("Workshop",     "Welcome, Agenda Setting &amp; Annual CV Check-In",     "Andrew"),
  s("Workshop",     "From Seminar Paper to Journal Article",                "Andrew"),
  s("Presentation", "Peer Research Presentations (Round 1)",                "All Students"),
  s("Workshop",     "Targeting the Right Journal",                          "Andrew"),
  s("Presentation", "Peer Research Presentations (Round 2)",                "All Students"),
  s("Workshop",     "Crafting an Argument and Contribution",                "Andrew"),
  s("Presentation", "Peer Research Presentations (Round 3)",                "All Students"),
  s("Workshop",     "ACSP Prep: Abstracts, Posters, Conference Strategy",   "Andrew"),
  s("Presentation", "Peer Research Presentations (Round 4)",                "All Students"),
  s("Workshop",     "Responding to Peer Review",                            "Andrew"),
  s("Presentation", "Peer Research Presentations (Round 5)",                "All Students"),
  s("Workshop",     "Co-authorship and Collaboration",                      "Andrew"),
  s("Student",      "TBD: Student-Initiated Session",                       "Students"),
  s("Break",        "Thanksgiving Break",                                   "&mdash;"),
  s("Synthesis",    "Semester Reflection &amp; Spring Preview",             "All")
)

spring_sessions <- rbind(
  s("Workshop",   "Welcome Back &amp; Spring Agenda Setting",               "Andrew"),
  s("Workshop",   "Proposal Structure &amp; Qualifying Packet / Exam",      "Andrew"),
  s("Milestone",  "Plan of Study Presentation (First-Year)",                "Cohort B"),
  s("Workshop",   "Theoretical Framework Development",                      "Andrew"),
  s("Milestone",  "Updated Plan of Study &amp; Annotated Bibliography",     "Cohort A"),
  s("Workshop",   "Methods Alignment and Justification",                    "Andrew"),
  s("Milestone",  "Qualifying Packet / Exam Content (Student 1)",           "Cohort A"),
  s("Workshop",   "Timeline, Feasibility &amp; Risk Management",            "Andrew"),
  s("Break",      "Spring Break",                                           "&mdash;"),
  s("Milestone",  "Qualifying Packet / Exam Content (Student 2)",           "Cohort A"),
  s("Workshop",   "Defending Your Work: Mock Defense / Exam Strategies",    "Andrew"),
  s("Student",    "TBD: Student-Initiated Session",                         "Students"),
  s("Conference", "ICUA/UAA Presentation Practice",                         "Students"),
  s("Break",      "ICUA/UAA Conference",                                    "&mdash;"),
  s("Synthesis",  "End of Year Celebration",                                "All")
)

tbl <- function(df) {
  knitr::kable(df, escape = FALSE, align = c("c", "l", "l", "l", "l"))
}
```

## Fall 2026

::: {.phase-header}
### Phase 1: Writing Your First Article
`r meeting_line(fall_start)`<br>`r date_span(fall_start, nrow(fall_sessions))`
:::

```{r}
#| label: fall-schedule
#| echo: false
tbl(build_schedule(fall_start, fall_sessions))
```

**Notes:** Core workshops alternate with student presentations. Week 13 is reserved for student-determined content. The final session connects fall article work to spring proposal development.

---

## Spring 2027

::: {.phase-header}
### Phase 3: Writing Your Dissertation Proposal
`r meeting_line(spring_start)`<br>`r date_span(spring_start, nrow(spring_sessions))`
:::

```{r}
#| label: spring-schedule
#| echo: false
tbl(build_schedule(spring_start, spring_sessions))
```

**Notes:** Milestone sessions accommodate both QRP and qualifying exam students. Week 12 is reserved for student-determined content. The seminar serves first- and second-year students together — Cohort A milestones are second-year work, Cohort B first-year.

---

## Session Types

- **<span class="badge-core">Workshop</span>** — Facilitated session on the semester's phase topic
- **<span class="badge-presentation">Presentation</span>** — Informal research-in-progress talk
- **<span class="badge-milestone">Milestone</span>** — Formal milestone presentation (Plan of Study, QRP, etc.)
- **<span class="badge-student">Student</span>** — Content determined by seminar participants
- **<span class="badge-conference">Conference</span>** — Conference preparation and presentation practice
- **<span class="badge-synthesis">Synthesis</span>** — Semester opening or closing session; reflection and forward planning
- **<span class="badge-break">Break</span>** — No seminar (holiday or conference)

---

*Schedule subject to change based on student needs and conference dates.*
